Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-09-11 ms/ms.qmd
First crack at writing intro section.

---
title: "Empowering use of preprints in ecology and evolution: an exploration of the first 1000 preprints of EcoEvoRxiv"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

>>>>

---
title: "Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints"
bibliography: ../bib/refs.bib
csl: ../bib/nature.csl
format:
  docx:
    reference-doc: ../bib/template.docx
editor_options: 
  chunk_output_type: console
execute:
  freeze: auto  # re-render only when source changes
  cache: false
  echo: false
  warning: false
  error: false
  include: true
crossref:
  fig-title: 'Figure'
  fig-labels: arabic
  title-delim: "-"
  fig-prefix: "Figure"
  tbl-prefix: "Table"
---

@@

# Introduction

Publishing preprints –- papers communicating non-peer-reviewed research findings –- are now an entrenched practice across a multitude of scientific disciplines in many countries. In ecology and evolution, new discpline specific preprint servers, such as *EcoEvoRxiv*, provide a means by which ecologists and evolutionary biologists can disemminate research findings, promoting open science practices (e.g., ensuring papers are open access) and facilitating the rapid sharing of new discoveries that can have significant impacts on fundamental and applied (e.g., conservation outcomes) knowledge globally. Improtantly, *EcoEvoRxiv* is a community driven preprint server that has paved the way for new inititives that attempt to break down barriers to scientific dissemination, including accepting multilanguage preprints (i.e., Spanish and Portuguese), recognising and accepting registered reports and promoting the use of peer review and community discuission to improve the quality of preprints (e.g., Peer Community In -- PCI).
